---
title: "ForLive_Unit1"
author: "Grace Lang"
date: "1/7/2021"
output: html_document
---

```{r setup, include=FALSE}
df <- read.csv('C://Users/david/OneDrive/Desktop/Time Series/TimeSeries_Spring21/Unit1/AustraliaTemp_1990.csv',header=TRUE)

df$Date <- as.Date(df$Date, format = "%m/%d/%y")

head(df)
##df$Year <- format(df$Date, "%Y")
###################################################################
library(readr)
df_all <- read_csv('C://Users/david/OneDrive/Desktop/Time Series/TimeSeries_Spring21/Unit1/AustraliaTemp_data.csv',col_names=TRUE,col_types = cols(Date = "D",Temp = "d"))

df_all$Date <- as.Date(df_all$Date, format = "%m/%d/%y")

head(df_all)


```

```{r}
plot(df, type = "linear")

library(ggplot2)
ggplot()+geom_line(data=df,aes(x=Date,y=Temp))

acf(df)
```
# Start of Unit 1 Homework 



## 1.2 
Figure 1.1a shows a plot of West Texas intermediate crude oil prices from
January 2000 to October, 2009, and Figure 1.19b shows monthly average
temperatures for Pennsylvania for January, 1990 to December, 2009. These
two data sets in tswge are wtcrude and patemp, respectively. For each of
these realizations, plot the sample autocorrelations, periodogram, and a
Parzen window-based spectral density estimate at the truncation point
. Explain how these plots describe (or fail to describe) the
behavior in the data
```{r}
library(tswge)
data(wtcrude)
data(patemp)

plot(wtcrude, type='linear')
acf(wtcrude)
#What is the periodogram?
parzen.wge(wtcrude)
plotts.sample.wge(wtcrude)

plot(patemp, type='linear')
acf(patemp)
parzen.wge(patemp)
plotts.sample.wge(patemp)

#Explain how these plots describe (or fail to describe) the behavior in the data
```

## 1.4
Following are displayed three sets of figures each containing four plots. The
first set shows four realizations of length n = 100 each generated from a time
series model. The second set contains four autocorrelation functions based
on the models used to generate realizations (in random order), and the third
set displays the four spectral densities. Match each realization with the
corresponding autocorrelations and spectral density. Explain your answers.